### 2023-04-04 reachable-resilience.tex
a first look at how 4.2 should be changed

The authors from \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}
have only been concerned with the case $\Safe = \uparrow \Safe$
and $\Bad =\downarrow \Bad$, 
\mathieu{pas tout à fait vrai: dans le technical report \cite{DBLP:conf/gg/Ozkan22} il considère aussi le cas où Bad et Safe sont tous les deux clos par le haut mais aussi le cas Safe clos par le bas Bad clos par le haut.}
 however as mentioned in Section~3
the property for instance of mutual exclusion is often modelised with $\Safe = \downarrow \Safe$.
Hence it makes sense to consider this symmetrical case as well. \\

\mathieu{rappeler résultats de \cite{DBLP:conf/gg/Ozkan22}}

\begin{definition}{marked WSTS} 
A {\em marked} WSTS is a tuple $(S, \leq, \to, INIT)$
where $(S, \leq, \to)$ is a WSTS and $INIT \subseteq S$. 
If $INIT$ is finite, we call it {\em fin-marked}.
\end{definition}

\begin{definition}
A marked WSTS is
\begin{itemize}
\item lossy if $\downarrow \post^* (INIT) = \post^* (INIT)$,
\item $\bot$-bounded (bottom-bounded) if there is a natural number 
$\ell \geq 0$ s.t. $s_B \in \post^{\leq \ell} (s) $ for every $ s \in S$ and every element 
$s_B$ of a basis of $S$ with $s \geq s_B$.
\end{itemize}
\end{definition}

\mathieu{}

\begin{theorem}{\cite{DBLP:conf/gg/Ozkan22}}
The bounded-state-resilience problem is decidable for \textcolor{red}{fin-marked} 
strongly compatible WSTS
 which are 
 {\em \textcolor{red}{lossy} } 
 and 
 {\em \textcolor{red}{$\bot$-bounded}  }
 if $\Bad = \uparrow \Bad$ and $\Safe = \downarrow \Safe$.
\end{theorem}

Unfortunately however the problem is undecidable in general.

@@

\mathieu{But what if we are in the case of $\uparrow \post^*$ effectiveness?}

\mathieu{Écrire que c'est globalement symmétrique au cas d'avant - je pense pas nécessairement qu'on arrive à faire beaucoup mieux que de juste dire ça.}

@@

Lemma~\ref{Lemma intersection 2} can be used to show that
$\post^*(s) \cap \Bad \subseteq D$  iff $ (\downarrow  \post^*(s)) \cap \Bad \subseteq D$.

If, as in Section~XX, we have the \textcolor{red}{added hypothesis}
that
$\pred^*(\Safe)$ is downward closed this means that
$\post^*(s) \cap \Bad \subseteq \pred^*(\Safe)$  iff $ (\downarrow  \post^*(s)) \cap \Bad \subseteq \pred^*(\Safe)$.

And hence decidability follows.

>>>>

Unfortunately the problem is undecidable in general.

@@

Despite this, "there is still hope". Indeed, in many ways the case where $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$
is symmetrical to the case $\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$.
%
For instance one can write the following lemma:

@@

In the case of a WSTS with downward compatiblitity, not necessarily strong,
then $\Safe$ downward-closed implies $\pred^*(\Safe)$ downward-closed and
Lemma~\ref{Lemma intersection 2} can be used to show that
if $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$,
then
$\post^*(s) \cap \Bad \subseteq \pred^*(\Safe)$  iff $ (\downarrow  \post^*(s)) \cap \Bad \subseteq \pred^*(\Safe)$.

\begin{theorem}
{\sc state-resilience} is decidable for WSTS with downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{theorem}

\mathieu{Maybe should discuss removing the assumption of upward compatibility and add a sort of 
$\downarrow \post^*$ effectiveness hypothesis, but what would it even mean ?}

\begin{proof}
Enumerate the downard-closed sets that contain $s$ and are closed under $\post$.
For ‘each of them’
check
intersection with $\Bad \subseteq \pred^*(\Safe)$.
If $(\downarrow  \post^*(s)) \cap \Bad \subseteq \pred^*(\Safe)$
then we know we will find some 
member of the enumeration such that
subseteq hold;
Conversely
compute

$$ \post(s), ~ \downarrow \post(s), \downarrow \post^2(s) \ldots $$

and ...

check whether at one point we encounter some element in $\Bad$ but not in $\pred^*(\Safe)$.

Strong downward compatibility implies furthermore the decidability
of $k$-state-resilience and bounded-state-resilience.

\iffalse	\mathieu{}

 The result from \cite{DBLP:journals/corr/abs-2108-00889}
only concerns with the case $\Safe = \uparrow \Safe$
and $\Bad =\downarrow \Bad$, 
 however as mentioned in Section~3
the property for instance of mutual exclusion is often modelised with $\Safe = \downarrow \Safe$.
Hence it makes sense to consider this symmetrical case as well. 
 \cite{DBLP:conf/gg/Ozkan22} considers 
 the case $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$ however the results are ...

\begin{definition}[marked WSTS] 
A {\em marked} WSTS is a tuple $(S, \leq, \to, s_0)$
where $(S, \leq, \to)$ is a WSTS and $s_0 \in S$. 
% If $INIT$ is finite, we call it {\em fin-marked}.
\end{definition}

\begin{definition}
A marked WSTS is
\begin{itemize}
\item lossy if $\downarrow \post^* (s_0) = \post^* (s_0)$,
\item $\bot$-bounded (bottom-bounded) if there is a natural number 
$\ell \geq 0$ s.t. $s_B \in \post^{\leq \ell} (s) $ for every $ s \in S$ and every element 
$s_B$ of a basis of $S$ with $s \geq s_B$.
\end{itemize}
\end{definition}

\begin{theorem}{\cite{DBLP:conf/gg/Ozkan22}}
The bounded-state-resilience problem is decidable for marked
strongly compatible WSTS
 which are 
 {\em \textcolor{red}{lossy} } 
 and 
 {\em \textcolor{red}{$\bot$-bounded}  }
 if $\Bad = \uparrow \Bad$ and $\Safe = \downarrow \Safe$.
\end{theorem}

\mathieu{}	\fi
